%Author: 
\documentclass[10pt, xcolor=x11names,compress]{beamer}
\usepackage{tabulary}
\usepackage{booktabs}
\usepackage{float}
\usepackage{graphicx}
\usepackage{mwe}% for example pictures
\usepackage{siunitx}
\usepackage{hyperref}

\usetheme{CambridgeUS}
\usecolortheme{seahorse}
\useoutertheme{infolines}
\usefonttheme[onlymath]{serif}
\setbeamertemplate{headline}[default]
\setbeamertemplate{navigation symbols}{}
\mode<beamer>{\setbeamertemplate{blocks}[rounded][shadow=true]}
\setbeamercovered{transparent}
\setbeamercolor{block body}{use=structure, fg=white, bg=black!20}
\setbeamercolor{itemize item}{fg=black}
\setbeamercolor{itemize subitem}{fg=gray} 
\setbeamercolor{itemize subsubitem}{fg=black!20} 
\makeatletter\setbeamertemplate{footline}
{  
\leavevmode%  
\hbox{%  
\begin{beamercolorbox}[wd=.333333\paperwidth,ht=2.25ex,dp=1ex,center]{author in head/foot}%    
\usebeamerfont{author in head/foot}
\insertshortauthor%~~\beamer@ifempty{\insertshortinstitute}{}
\insertshortinstitute{Int. MSc. NISER}
 \end{beamercolorbox}%  
 \begin{beamercolorbox}[wd=.333333\paperwidth,ht=2.25ex,dp=1ex,center]{institute in head/foot}%    
 \usebeamerfont{title in head/foot}\insertinstitute  
 \end{beamercolorbox}%  
 \begin{beamercolorbox}[wd=.333333\paperwidth,ht=2.25ex,dp=1ex,right]{date in head/foot}%    
 \usebeamerfont{date in head/foot}\insertshortdate{}\hspace*{2em}    
 \insertframenumber{} / \inserttotalframenumber\hspace*{2ex}   
 \end{beamercolorbox}}%  
 \vskip0pt%
 }
 \makeatother 
 \useoutertheme[footline=empty, subsection=false]{miniframes}
 \usepackage{multicol}  
 
 \begin{document}

\section{Slide 1}
\begin{frame}[label=Background]{\centerline {Analyzing Strategies for } \centerline{Voronoi Area Game}}
\begin{center}
    \textbf{Samir Dileep \& Sandipan Samanta}
\end{center}
\begin{itemize}
    \item \underline{\textbf{Idea:}} Predict optimal moves for victory in the Voronoi diagram area game and analyse resulting patterns.
    \item \underline{\textbf{Dataset:}} Self-made data-set by simulating in-house version of said game.
    \item \underline{\textbf{Relevant Papers:}}
              \begin{enumerate}
              \scriptsize
                  \item \href{https://doi.org/10.1007/978-3-642-31866-5_9}{\textit{MCTS Experiments on the Voronoi Game}}\\
                  Bouzy, B., Métivier, M., Pellier, D. \\In: van den Herik, H.J., Plaat, A. (eds) Advances in Computer Games. ACG 2011. Lecture Notes in Computer Science, vol 7168. Springer, Berlin, Heidelberg.
                  \item \href{https://doi.org/10.1016/j.comgeo.2017.02.003}{\textit{The Discrete Voronoi Game in ${\rm I\!R}^2$}}\\
                  Aritra Banik, Bhaswar B. Bhattacharya, Sandip Das, Satyaki Mukherjee\\
                  Computational Geometry, Volume 63, 2017, Pages 53-62, ISSN 0925-7721.

              \end{enumerate}

    
\end{itemize} 
\vspace{18pt}
\end{frame}

\section{Slide 2}
\begin{frame}{}
\begin{itemize}
    \item \underline{\textbf{Work Distribution:}}
    \begin{itemize}
        \item{Samir:} Literature review on vaible ML algorithms, generating corresponding dataset.
        \item{Sandipan:} Literature review on Computational Geometry and expected patterns in observations.
        \item{Both:} Slides, Reports, and Implementation of Algorithms.
    \end{itemize}
    \item \underline{\textbf{Goals for Mid-term:}}
    \begin{itemize}
        \item Curating data-set and organisation.
        \item Implementation, optimization and comparison of different ML algorithms on simulatory dataset.
    \end{itemize}
        \item \underline{\textbf{Expected Results:}}
    \begin{itemize}
        \item Optimal prediction with high win-rate against test data.
    \end{itemize}
\end{itemize}

\end{frame}


\end{document}
